Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-10-13 write_up/highlights.tex
Final steps before submission

	\item one
	\item two
	\item three
	\item four
	\item five 
	\item six

>>>>

	\item We developed a highly spatially resolved discrete-event
		simulation model of mixed fishery interactions with multiple
		populations.	
	\item The simulation framework incorporates i) delay-difference population
		dynamics, ii) population movement using Gaussian Markov Fields
		to simulate patchy, heterogeneously distribution populations,
		and iii) individual-based fishery dynamics for multiple fleet
		characteristics using an explore-exploit strategy.
	\item The framework allows users to explore assumptions in modelling
		observational data and examine dynamics at a fine
		spatiotemporal scale. 
	\item We simulate fifty years of multiple fisheries exploiting four
		separate populations with different demographics and find
		nuanced spatio-temporal patterns in exploitation.
	\item A simulated spatial closure shows that when aggregating point
		data on fishing activity to a grid, the scale of aggregation
		matters for the ability to achieve fishery-conservation
		objectives.
	\item The simulation framework is available as an R package and we
		suggest multiple potential uses of the package (e.g. survey
		design evaluation, testing index standardisation, in-year
		fishery and biological modelling) for researchers.

### 2019-10-13 write_up/mixfishsim_ecolmod.tex
Final steps before submission

\begin{keyword}
spatiotemporal \sep mixed fisheries \sep individual based \sep spatial
management \sep homogeneity \sep  preferential sampling
\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

The aggregated catch composition from each of the data sources over a ten-year
period (which shows average seasonal patterns) at different spatial resolutions
highlights different patterns in perceived community structure depending on the
data source and aggregation level (Figure \ref{fig:1}). The finer spatial grid
for the true population (top left) and commercial data (top middle) show
visually similar patterns, though there are large unsampled areas in the
commercial data from a lack of fishing activity (particularly in the lower left
part of the sampling domain). The survey data at this spatial resolution
displays very sparse information about the spatial distributions of the
populations. The slightly aggregated data on a 5 x 5 grid shows similar
patterns and, while losing some of the spatial detail, there remains good
consistency between the true population and the commercial data. Survey data
starts to pick out some of the similar patterns as the other data sources, but
lacks spatiotemporal coverage. The spatial catch information on a 10 x 10 and
20 x 20 grid lose a significant amount of information about the spatial
resolutions for all data sources, and some differences between the survey,
commercial and true population data emerge. \\

@@

\section*{CRediT author statement} \textbf{Paul Dolder:} Conceptualisation,
methodology, software, writing - original draft. \textbf{Cóilín Minto:}
Conceptualisation, Methodology, writing - review and editing, supervision,
funding acquisition. textbf{Jean-Marc Guarini:} methodology, writing - review
and editing, funding acquisition, supervision. \textbf{Jan Jaap Poos:}
methodology, writing - review and editing, supervision. \

>>>>

\begin{keyword}
spatiotemporal \sep mixed fisheries \sep individual based \sep spatial
management \sep heterogeneity \sep  preferential sampling
\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

The aggregated catch composition from each of the data sources over a ten-year
period (which shows average seasonal patterns) at different spatial resolutions
highlights different patterns in perceived community structure depending on the
data source and aggregation level (Figure \ref{fig:1}; visualised using
\cite{Gerritsen2014}). The finer spatial grid for the true population (top
left) and commercial data (top middle) show visually similar patterns, though
there are large unsampled areas in the commercial data from a lack of fishing
activity (particularly in the lower left part of the sampling domain). The
survey data at this spatial resolution displays very sparse information about
the spatial distributions of the populations. The slightly aggregated data on a
5 x 5 grid shows similar patterns and, while losing some of the spatial detail,
there remains good consistency between the true population and the commercial
data. Survey data starts to pick out some of the similar patterns as the other
data sources, but
lacks spatiotemporal coverage. The spatial catch information on a 10 x 10 and
20 x 20 grid lose a significant amount of information about the spatial
resolutions for all data sources, and some differences between the survey,
commercial and true population data emerge. \\

@@
